### 2018-09-10 acks.tex
Word hard wrap 80 col

The authors would like to thank  members of Advanced Reactors and Fuel Cycles
research group (ARFC) at the University of Illinois - Urbana Champaign who 
provided valuable code reviews and proofreading.

The authors contributed to this work as described below.  Andrei Rykhlevskii 
conceived and designed the simulations, wrote the paper, prepared figures 
and/or tables, performed the computation work, contributed to the software 
product, and reviewed drafts of the paper. Jin Whan Bae conceived and designed 
the simulations, wrote the paper, contributed to the software 
product, and reviewed drafts of the paper. Andrei Rykhlevskii and Jin Whan Bae 
is supported by the Department of Nuclear, Plasma, and Radiological Engineering.

>>>>

The authors would like to thank  members of the \gls{ARFC} group at the 
University of Illinois - Urbana Champaign who provided valuable code reviews 
and proofreading.

The authors contributed to this work as described below.  Andrei Rykhlevskii 
conceived and designed the simulations, wrote the paper, prepared figures 
and/or tables, performed the computation work, contributed to the software 
product, and reviewed drafts of the paper. Jin Whan Bae conceived and designed 
the simulations, wrote the paper, contributed to the software 
product, and reviewed drafts of the paper. Andrei Rykhlevskii 
is supported by the Department of Nuclear, Plasma, and Radiological 
Engineering. Jin Whan Bae is supported by funding received from the DOE Office 
of Nuclear Energy's Nuclear Energy University Program (Project 16-10512) 
`Demand-Driven Cycamore Archetypes'.

### 2018-09-10 results.tex

\subsection{Neutron flux}
Figure~\ref{fig:radial_flux} shows the radial distribution of fast and thermal 
neutron flux for the both initial and equilibrium composition. The neutron fluxes
have similar shapes for both compositions but the equilibrium case has a harder 
spectrum. A significant spectral shift was observed in the central region of 
the core (zone I), while for the outer region (zone II), it is negligible for fast 
but notable for thermal neutrons. These neutron flux radial distributions are in 
good agreement with original ORNL report \cite{robertson_conceptual_1971}. 
Overall, spectrum hardening during \gls{MSBR} operation should be carefully 
studied when designing the reactivity control system.
\begin{figure}[ht!] % replace 't' with 'b' to force it to \centering
  \includegraphics[width=\textwidth]{radial_flux.png} \caption{Radial neutron 
  flux distribution for initial and equilibrium fuel salt composition.}
  \label{fig:radial_flux}
\end{figure}

@@

generated in zone I except the majority of $^{233}$Th that is 

>>>>

\subsection{Neutron flux}
Figure~\ref{fig:radial_flux} shows the radial distribution of fast and thermal 
neutron flux for the both initial and equilibrium composition. The neutron fluxes
have similar shapes for both compositions but the equilibrium case has a harder 
spectrum. A significant spectral shift was observed in the central region of 
the core (zone I), while for the outer region (zone II), it is negligible for fast 
but notable for thermal neutrons. These neutron flux radial distributions 
agree with the fluxes in the original ORNL report \cite{robertson_conceptual_1971}. 
Overall, spectrum hardening during \gls{MSBR} operation should be carefully 
studied when designing the reactivity control system.
\begin{figure}[ht!] % replace 't' with 'b' to force it to \centering
  \includegraphics[width=\textwidth]{radial_flux.png} \caption{Radial neutron 
  flux distribution for initial and equilibrium fuel salt composition.}
  \label{fig:radial_flux}
\end{figure}

@@

generated in zone I and the majority of $^{233}$Th is 
